UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio and Reconfigurable Intelligent Surface

### 2022-08-10 main.tex
:pencil: Update notations

% dark mode
% \usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}

@@

	\emph{Notations:} Scalars, vectors and matrices are respectively denoted by italic, bold lower-case, and bold upper-case letters.
	$j$ represents the imaginary unit.
	% $\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix.
	% $\boldsymbol{I}$ represents the identity matrix.
	% $\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the space of real nonnegative and complex $x \times y$ matrices.
	$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ respectively denote the space of real nonnegative and complex $x \times y$ matrices.
	% $\Re\{\cdot\}$ retrieves the real part of a complex entity. $[\cdot]_{(n)}$ denotes the $n$-th entry of a vector and $[\cdot]_{(1:n)}$ denotes the first $n$ entries of a vector.
	$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ respectively represent the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm.
	% $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ respectively denote the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix.
	% $\odot$ denotes the Hadamard product.
	% $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite.
	% $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal.
	% $\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t. random variable $X$ ($X$ is omitted for simplicity).
	The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$.
	$\sim$ means ``distributed as''.
	$(\cdot)^{(i)}$ represents the $i$-th iterated value and $(\cdot)^{\star}$ represents the end solution.
\end{section}

>>>>

% dark mode
\usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}

@@

	\emph{Notations:}
	Italic, bold lower-case, and bold upper-case letters denote scalars, vectors and matrices, respectively.
	$\boldsymbol{0}$ and $\boldsymbol{1}$ denote zero and one array of appropriate size, respectively.
	$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote the real nonnegative and complex spaces of dimension $x \times y$, respectively.
	$j$ denotes the imaginary unit.
	$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $\lvert{\cdot}\rvert$, and $\lVert{\cdot}\rVert$ denote the conjugate, transpose, conjugate transpose, absolute value, and Euclidean norm operators, respectively.
	$(\cdot)^{(r)}$ and $(\cdot)^{\star}$ denote the $r$-th iterated and terminal solutions, respectively.
	The distribution of a \gls{cscg} random variable with zero mean and variance $\sigma^2$ is denoted by $\mathcal{CN}(0,\sigma^2)$, and $\sim$ means ``distributed as''.
\end{section}
